---
title: "LaserCutterPredict"
subtitle: "A new way to estimate laser cutter parameters."
author: "Franck Bettinger"
highlighter: highlight.js
output: pdf_document
knit: slidify::knit2slides
mode: selfcontained
hitheme: tomorrow
framework: io2012
widgets: []
---

## The problem

1. Laser cutter parameters are hard to estimate
2. Tests are needed 
  * waste of time
  * waste of material
  * potential fire (safety issue)
3. When using differents materials
  * parameters are hard to remember
  * making a list could be long
4. When using different thicknesses
  * different power
  * different speed

---

## The solution

1. Create a database of parameters
  * for different materials
  * for different thicknesses
  
2. Estimate parameters for a material
  * find the closest match (with power median speed)
  * find power for different speeds (saving time)
  * give only power values the machine can deliver
  
3. Estimate parameters for thicknesses
  * when the material has been used before
  * when that thickness is not in the database
  * by linear regression

---

## The software

1. Multilangual (English / French)

2. Add/download known laser cutter parameters

3. Predictions and a graph to check linear assumption

```{r echo=FALSE, fig.width= 6, fig.height=5, fig.align='center'}

library(ggplot2)
library(reshape2)

  data<-read.csv("../parameters.csv",
                 stringsAsFactors = FALSE)

  d<-data[data$material=="MDF"&data$thickness==6&data$cuttype=="Decoupe"&!is.na(data$minpuiss)&!is.na(data$maxpuiss),]
  names(d)<-c("date","seller","material","thickness","cuttype","speed","min","max")
  
  if (dim(d)[[1]]>1)
  {
  dMelt<-melt(d,measure.vars=c("min", "max"), id.vars=c("speed"))
  
  qplot(speed, value, data=dMelt, 
          col=variable, geom=c("point", "smooth"), 
          method="lm",
          xlab="Speed", 
          ylab="Power", 
          main="Decoupe MDF 6mm"
          )+ theme(legend.title = element_blank())
          
  }
```

---

## Example of prediction by thickness

1. Example of computed values for a MDF cut

```{r xtable, echo=FALSE, results='asis'}
library(xtable)
data<-read.csv("../parameters.csv",
                 stringsAsFactors = FALSE)
  
  d<-data[data$material=="MDF" &data$cuttype=="Decoupe"&!is.na(data$minpuiss)&!is.na(data$maxpuiss),]
 
  speedFit<-lm(speed~thickness, data = d)
  minFit<-lm(minpuiss~thickness, data = d)
  maxFit<-lm(maxpuiss~thickness, data = d)
  thicknesses<-seq(1,10,1)
  speeds<-predict(speedFit, newdata = data.frame(thickness=thicknesses))
  mins<-predict(minFit, newdata = data.frame(thickness=thicknesses))
  maxs<-predict(maxFit, newdata = data.frame(thickness=thicknesses))
  data2<-data.frame(thickness= thicknesses, speed=speeds, minpuiss=mins, maxpuiss=maxs)
  # keep only the meaningful values (100>=power>=10 and max>=min)
  data2<- data2[data2$maxpuiss<=100&data2$maxpuiss>=data2$minpuiss&data2$minpuiss>=10&data2$speed>0,]
  
  names(data2)<- c("Thickness", "Speed","Minimum power","Maximum power")
  

  print(xtable(data2), type = "html")
```


 * Values above 6mm are not show because the laser cutter is not powerful enough to cut above. No need to try -> saves time and material.

 * The tickness value of 1mm is not shown because the linear regression gives a minimum power value less than the minimum the laser can deliver.



